 Allocation scoring rules as a generalization of quantile scoring rules

### 2023-06-06 notes/allocation_notes.rmd
another correction in quantile scoring rule section

By making the forecaster aware of $s$ prior to prediction, we elicit an $\alpha$-level quantile $q_{\alpha,F}$ of the forecast distribution $F$ for $Y$, 
where $\alpha = U/(U+O)$. To see this, notice that if a forecaster believes that $Y \sim F$, they will calculate their expected score to be
\begin{align} 
\sbar_F(x) = E_F[s(x,Y)]  &= O E_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(Y) - g(x))\sb{+}]. \label{eqn:scalar_obj}
\end{align}
In order to minimize this expectation, they must forecast a solution of the first order equation
\begin{align}
\nonumber 0 =\frac{d}{dx}\sbar_F(x) 
&= O E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{+}\right] + U E_F\left[\frac{d}{dx}(g(Y) - g(x))\sb{+}\right] \\
&= O E_F[g^{\prime}(x)\mathbb{1}\{Y < x\}] + U E_F[-g^{\prime}(x)\mathbb{1}\{Y \geq x\}] \\
&= O g^{\prime}(x) \mathbb{P}_F(Y<x) - U g^{\prime}(x) \mathbb{P}_F(Y\geq x) \\
&= g^{\prime}(x)\left( O F(x) - U (1-F(x))\right) \\
&= (O+U) g^{\prime}(x)\left(F(x) - \alpha\right), \label{scalar_Z_deriv}
\end{align}
that is, a quantile $q_{\alpha, F} \in Q_F\left(\alpha\right)$.
(See \hyperref[scalar_Z_deriv_detail]{appendix} for an alternative derivation in terms of a density.)
The critical point $q_{\alpha, F}$ is actually a minimum since \eqref{scalar_Z_deriv} is non-positive on $\{x<q_{\alpha, F}\}$ and non-negative on $\{x>q_{\alpha, F}\}$.
 With the assumptions that $g^{\prime}(q)>0$ and that $Q_F\left(\alpha\right)$ is the singleton $\{q_{\alpha, F}\}$, this minimum is unique since
\begin{align}
\frac{d^2}{dx^2}\sbar_F(x)\big|_{x=q_{\alpha, F}} 
&= (O+U)\left(g^{\prime}(x)f(x) + g^{\prime \prime}(x)\left(F(x) - \alpha\right)\right)\big|_{x=q_{\alpha, F}} \label{scalar_Z_deriv2}\\
&= (O+U)(g^{\prime}(q_{\alpha, F})f(q_{\alpha, F}) + g^{\prime \prime}(q_{\alpha, F})\cdot 0) >0.
\end{align}

>>>>

By making the forecaster aware of $s$ prior to prediction, we elicit an $\alpha$-level quantile $q_{\alpha,F}$ of the forecast distribution $F$ for $Y$, 
where $\alpha = U/(U+O)$. To see this, notice that if a forecaster believes that $Y \sim F$, they will calculate their expected score to be
\begin{align} 
\sbar_F(x) = E_F[s(x,Y)]  &= O E_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(Y) - g(x))\sb{+}]. \label{eqn:scalar_obj}
\end{align}
In order to minimize this expectation, they must forecast a solution of the first order equation
\begin{align}
\nonumber 0 =\frac{d}{dx}\sbar_F(x) 
&= O E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{+}\right] + U E_F\left[\frac{d}{dx}(g(Y) - g(x))\sb{+}\right] \\
&= O E_F[g^{\prime}(x)\mathbb{1}\{Y < x\}] + U E_F[-g^{\prime}(x)\mathbb{1}\{Y \geq x\}] \\
&= O g^{\prime}(x) \mathbb{P}_F(Y<x) - U g^{\prime}(x) \mathbb{P}_F(Y\geq x) \\
&= g^{\prime}(x)\left( O F(x) - U (1-F(x))\right) \\
&= (O+U) g^{\prime}(x)\left(F(x) - \alpha\right), \label{scalar_Z_deriv}
\end{align}
that is, a quantile $q_{\alpha, F} \in Q_F\left(\alpha\right)$.
(See \hyperref[scalar_Z_deriv_detail]{appendix} for an alternative derivation in terms of a density.)
The critical point $q_{\alpha, F}$ is actually a minimum since \eqref{scalar_Z_deriv} is non-positive on $\{x< \inf\left(Q_F\left(\alpha\right)\right)\}$ and non-negative on $\{x>\sup\left(Q_F\left(\alpha\right)\right)\}$.
 With the assumptions that $g^{\prime}(q)>0$ and that $Q_F\left(\alpha\right)$ is the singleton $\{q_{\alpha, F}\}$, this minimum is unique since
\begin{align}
\frac{d^2}{dx^2}\sbar_F(x)\big|_{x=q_{\alpha, F}} 
&= (O+U)\left(g^{\prime}(x)f(x) + g^{\prime \prime}(x)\left(F(x) - \alpha\right)\right)\big|_{x=q_{\alpha, F}} \label{scalar_Z_deriv2}\\
&= (O+U)(g^{\prime}(q_{\alpha, F})f(q_{\alpha, F}) + g^{\prime \prime}(q_{\alpha, F})\cdot 0) >0.
\end{align}
